---
title: "inspect_imputation_accuracies"
output: html_document
---

# Summary statistics of accuracies

```{r}

acc <- read.delim("../data/output/jhu_abr/masked/accuracies.txt", head=T, stringsAsFactors = F)
acc[(is.na(acc$prop_match)),]
summary(acc$prop_match)
pr <- read.delim("../data/output/jhu_abr/masked/precision_recall.txt", head=T, stringsAsFactors = F)
summary(pr$precision)
summary(pr$recall)

acc <- read.delim("../data/output/ucsf_pr/masked/accuracies.txt", head=T, stringsAsFactors = F)
acc[(is.na(acc$prop_match)),]
summary(acc$prop_match)
pr <- read.delim("../data/output/ucsf_pr/masked/precision_recall.txt", head=T, stringsAsFactors = F)
summary(pr$precision)
summary(pr$recall)

acc <- read.delim("../data/output/washington/masked/accuracies.txt", head=T, stringsAsFactors = F)
acc[(is.na(acc$prop_match)),]
summary(acc$prop_match)
pr <- read.delim("../data/output/washington/masked/precision_recall.txt", head=T, stringsAsFactors = F)
summary(pr$precision)
summary(pr$recall)

acc <- read.delim("../data/output/washington/masked/accuracies_tgp.txt", head=T, stringsAsFactors = F)
acc[(is.na(acc$prop_match)),]
summary(acc$prop_match)
pr <- read.delim("../data/output/washington/masked/precision_recall_tgp.txt", head=T, stringsAsFactors = F)
summary(pr$precision)
summary(pr$recall)

```


# Histogram of accuracies

```{r}

acc <- read.delim("../data/output/jhu_abr/masked/accuracies.txt", head=T, stringsAsFactors = F)
hist(acc$prop_match, main="jhu_abr", breaks = 20)
pr <- read.delim("../data/output/jhu_abr/masked/precision_recall.txt", head=T, stringsAsFactors = F)
hist(pr$precision, main="jhu_abr", breaks = 20)
hist(pr$recall, main="jhu_abr", breaks = 20)

acc <- read.delim("../data/output/washington/masked/accuracies.txt", head=T, stringsAsFactors = F)
hist(acc$prop_match, main="washington", breaks = 20)
pr <- read.delim("../data/output/washington/masked/precision_recall.txt", head=T, stringsAsFactors = F)
hist(pr$precision, main="washington", breaks = 20)
hist(pr$recall, main="washington", breaks = 20)

acc <- read.delim("../data/output/washington/masked/accuracies.txt", head=T, stringsAsFactors = F)
hist(acc$prop_match, main="washington", breaks = 20)
pr <- read.delim("../data/output/washington/masked/precision_recall.txt", head=T, stringsAsFactors = F)
hist(pr$precision, main="washington", breaks = 20)
hist(pr$recall, main="washington", breaks = 20)

acc <- read.delim("../data/output/washington/masked/accuracies_tgp.txt", head=T, stringsAsFactors = F)
hist(acc$prop_match, main="washington_tgp", breaks = 20)
pr <- read.delim("../data/output/washington/masked/precision_recall_tgp.txt", head=T, stringsAsFactors = F)
hist(pr$precision, main="washington_tgp", breaks = 20)
hist(pr$recall, main="washington_tgp", breaks = 20)

```

# Plot accuracies against MAF

```{r}

acc <- read.delim("../data/output/jhu_abr/masked/accuracies.txt", head=T, stringsAsFactors = F)
plot(acc$MAF, acc$prop_match, main="jhu_abr")
pr <- read.delim("../data/output/jhu_abr/masked/precision_recall.txt", head=T, stringsAsFactors = F)
plot(pr$MAF, pr$precision, main="jhu_abr")

acc <- read.delim("../data/output/ucsf_pr/masked/accuracies.txt", head=T, stringsAsFactors = F)
plot(acc$MAF, acc$prop_match, main="ucsf_pr")
pr <- read.delim("../data/output/ucsf_pr/masked/precision_recall.txt", head=T, stringsAsFactors = F)
plot(pr$MAF, pr$precision, main="ucsf_pr")

acc <- read.delim("../data/output/washington/masked/accuracies_tgp.txt", head=T, stringsAsFactors = F)
plot(acc$MAF, acc$prop_match, main="washington_tgp")
pr <- read.delim("../data/output/washington/masked/precision_recall.txt", head=T, stringsAsFactors = F)
plot(pr$MAF, pr$precision, main="washington_tgp")


```

# Plot accuracies against Rsq

```{r}

acc <- read.delim("../data/output/jhu_abr/masked/accuracies.txt", head=T, stringsAsFactors = F)
plot(acc$Rsq, acc$prop_match, main="jhu_abr")
pr <- read.delim("../data/output/jhu_abr/masked/precision_recall.txt", head=T, stringsAsFactors = F)
plot(pr$Rsq, pr$precision, main="jhu_abr")

acc <- read.delim("../data/output/ucsf_pr/masked/accuracies.txt", head=T, stringsAsFactors = F)
plot(acc$Rsq, acc$prop_match, main="ucsf_pr")
pr <- read.delim("../data/output/ucsf_pr/masked/precision_recall.txt", head=T, stringsAsFactors = F)
plot(pr$Rsq, pr$precision, main="ucsf_pr")

acc <- read.delim("../data/output/washington/masked/accuracies.txt", head=T, stringsAsFactors = F)
plot(acc$Rsq, acc$prop_match, main="washington")
pr <- read.delim("../data/output/washington/masked/precision_recall.txt", head=T, stringsAsFactors = F)
plot(pr$Rsq, pr$precision, main="washington")

acc <- read.delim("../data/output/washington/masked/accuracies_tgp.txt", head=T, stringsAsFactors = F)
plot(acc$Rsq, acc$prop_match, main="washington_tgp")
pr <- read.delim("../data/output/washington/masked/precision_recall_tgp.txt", head=T, stringsAsFactors = F)
plot(pr$Rsq, pr$precision, main="washington_tgp")
```

### Boxplots of accuracy by site

jhu_abr does best; ucsf_pr and washington seems similar; washington_tgp looks slightly better than washington

#### Overall

```{r}

acc.all <- read.delim("../data/output/jhu_abr/masked/accuracies.txt", head=T, stringsAsFactors = F)
acc.all$site <- "jhu_abr"

acc <- read.delim("../data/output/ucsf_pr/masked/accuracies.txt", head=T, stringsAsFactors = F)
acc$site <- "ucsf_pr"
acc.all <- rbind(acc.all, acc)

acc <- read.delim("../data/output/washington/masked/accuracies.txt", head=T, stringsAsFactors = F)
acc$site <- "washington"
acc.all <- rbind(acc.all, acc)

acc <- read.delim("../data/output/washington/masked/accuracies_tgp.txt", head=T, stringsAsFactors = F)
acc$site <- "washington_tgp"
acc.all <- rbind(acc.all, acc)

boxplot(prop_match ~ site, data=acc.all)
```

#### Split into 4 Rsq bins

washington_tgp does better for the lower Rsq bins, not really for the highest quality bin.

```{r}

par(mfrow=c(2,2))

bin1.acc <- acc.all[acc.all$Rsq <= 0.25,]
bin2.acc <- acc.all[(acc.all$Rsq > 0.25) & (acc.all$Rsq <= 0.5),]
bin3.acc <- acc.all[(acc.all$Rsq > 0.5) & (acc.all$Rsq <= 0.75),]
bin4.acc <- acc.all[(acc.all$Rsq > 0.75) & (acc.all$Rsq <= 1),]

boxplot(prop_match ~ site, data=bin1.acc, main="Rsq [0.00 - 0.25]")
boxplot(prop_match ~ site, data=bin2.acc, main="Rsq (0.25 - 0.50]")
boxplot(prop_match ~ site, data=bin3.acc, main="Rsq (0.50 - 0.75]")
boxplot(prop_match ~ site, data=bin4.acc, main="Rsq (0.75 - 1.00]")

barplot(c(sum(bin1.acc$site=="jhu_abr", na.rm=T)/sum(acc.all$site == "jhu_abr"), 
          sum(bin1.acc$site=="ucsf_pr", na.rm=T)/sum(acc.all$site == "ucsf_pr"), 
          sum(bin1.acc$site=="washington", na.rm=T)/sum(acc.all$site == "washington"), 
          sum(bin1.acc$site=="washington_tgp", na.rm=T)/sum(acc.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="Rsq [0.00 - 0.25]")
barplot(c(sum(bin2.acc$site=="jhu_abr", na.rm=T)/sum(acc.all$site == "jhu_abr"), 
          sum(bin2.acc$site=="ucsf_pr", na.rm=T)/sum(acc.all$site == "ucsf_pr"), 
          sum(bin2.acc$site=="washington", na.rm=T)/sum(acc.all$site == "washington"), 
          sum(bin2.acc$site=="washington_tgp", na.rm=T)/sum(acc.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="Rsq [0.25 - 0.50]")
barplot(c(sum(bin3.acc$site=="jhu_abr", na.rm=T)/sum(acc.all$site == "jhu_abr"), 
          sum(bin3.acc$site=="ucsf_pr", na.rm=T)/sum(acc.all$site == "ucsf_pr"), 
          sum(bin3.acc$site=="washington", na.rm=T)/sum(acc.all$site == "washington"), 
          sum(bin3.acc$site=="washington_tgp", na.rm=T)/sum(acc.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="Rsq [0.50 - 0.75]")
barplot(c(sum(bin4.acc$site=="jhu_abr", na.rm=T)/sum(acc.all$site == "jhu_abr"), 
          sum(bin4.acc$site=="ucsf_pr", na.rm=T)/sum(acc.all$site == "ucsf_pr"), 
          sum(bin4.acc$site=="washington", na.rm=T)/sum(acc.all$site == "washington"), 
          sum(bin4.acc$site=="washington_tgp", na.rm=T)/sum(acc.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="Rsq [0.75 - 1.00]")

```

#### Subset into the MAF and Rsq BINs you used for filtering

How many more SNPs do you loose with Washington TGP for Rsq filters

```{r}

par(mfrow=c(2,2))

bin1.acc <- acc.all[(acc.all$MAF<= 0.005) & (acc.all$Rsq <= 0.5),]
bin2.acc <- acc.all[(acc.all$MAF<= 0.005) & (acc.all$Rsq > 0.5),]
bin3.acc <- acc.all[(acc.all$MAF > 0.005) & (acc.all$Rsq <= 0.3),]
bin4.acc <- acc.all[(acc.all$MAF > 0.005) & (acc.all$Rsq > 0.3),]

boxplot(prop_match ~ site, data=bin1.acc, main="MAF <= 0.005 Rsq <= 0.5")
boxplot(prop_match ~ site, data=bin2.acc, main="MAF <= 0.005 Rsq > 0.5")
boxplot(prop_match ~ site, data=bin3.acc, main="MAF > 0.005 Rsq <= 0.3")
boxplot(prop_match ~ site, data=bin4.acc, main="MAF > 0.005 Rsq > 0.3")

barplot(c(sum(bin1.acc$site=="jhu_abr", na.rm=T)/sum(acc.all$site == "jhu_abr"), 
          sum(bin1.acc$site=="ucsf_pr", na.rm=T)/sum(acc.all$site == "ucsf_pr"), 
          sum(bin1.acc$site=="washington", na.rm=T)/sum(acc.all$site == "washington"), 
          sum(bin1.acc$site=="washington_tgp", na.rm=T)/sum(acc.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="MAF <= 0.005 Rsq <= 0.5")
barplot(c(sum(bin2.acc$site=="jhu_abr", na.rm=T)/sum(acc.all$site == "jhu_abr"), 
          sum(bin2.acc$site=="ucsf_pr", na.rm=T)/sum(acc.all$site == "ucsf_pr"), 
          sum(bin2.acc$site=="washington", na.rm=T)/sum(acc.all$site == "washington"), 
          sum(bin2.acc$site=="washington_tgp", na.rm=T)/sum(acc.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="MAF <= 0.005 Rsq > 0.5")
barplot(c(sum(bin3.acc$site=="jhu_abr", na.rm=T)/sum(acc.all$site == "jhu_abr"), 
          sum(bin3.acc$site=="ucsf_pr", na.rm=T)/sum(acc.all$site == "ucsf_pr"), 
          sum(bin3.acc$site=="washington", na.rm=T)/sum(acc.all$site == "washington"), 
          sum(bin3.acc$site=="washington_tgp", na.rm=T)/sum(acc.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="MAF > 0.005 Rsq <= 0.3")
barplot(c(sum(bin4.acc$site=="jhu_abr", na.rm=T)/sum(acc.all$site == "jhu_abr"), 
          sum(bin4.acc$site=="ucsf_pr", na.rm=T)/sum(acc.all$site == "ucsf_pr"), 
          sum(bin4.acc$site=="washington", na.rm=T)/sum(acc.all$site == "washington"), 
          sum(bin4.acc$site=="washington_tgp", na.rm=T)/sum(acc.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="MAF > 0.005 Rsq > 0.3")

```

### Boxplots of precision by site

#### Overall

```{r}
pr.all <- read.delim("../data/output/jhu_abr/masked/precision_recall.txt", head=T, stringsAsFactors = F)
pr.all$site <- "jhu_abr"

pr <- read.delim("../data/output/ucsf_pr/masked/precision_recall.txt", head=T, stringsAsFactors = F)
pr$site <- "ucsf_pr"
pr.all <- rbind(pr.all, pr)

pr <- read.delim("../data/output/washington/masked/precision_recall.txt", head=T, stringsAsFactors = F)
pr$site <- "washington"
pr.all <- rbind(pr.all, pr)

pr <- read.delim("../data/output/washington/masked/precision_recall_tgp.txt", head=T, stringsAsFactors = F)
pr$site <- "washington_tgp"
pr.all <- rbind(pr.all, pr)

boxplot(precision ~ site, data=pr.all)
```

#### Split into 4 Rsq bins

```{r}

par(mfrow=c(2,2))

bin1.pr <- pr.all[pr.all$Rsq <= 0.25,]
bin2.pr <- pr.all[(pr.all$Rsq > 0.25) & (pr.all$Rsq <= 0.5),]
bin3.pr <- pr.all[(pr.all$Rsq > 0.5) & (pr.all$Rsq <= 0.75),]
bin4.pr <- pr.all[(pr.all$Rsq > 0.75) & (pr.all$Rsq <= 1),]

boxplot(precision ~ site, data=bin1.pr, main="Rsq [0.00 - 0.25]")
boxplot(precision ~ site, data=bin2.pr, main="Rsq (0.25 - 0.50]")
boxplot(precision ~ site, data=bin3.pr, main="Rsq (0.50 - 0.75]")
boxplot(precision ~ site, data=bin4.pr, main="Rsq (0.75 - 1.00]")

barplot(c(sum(bin1.pr$site=="jhu_abr", na.rm=T)/sum(pr.all$site == "jhu_abr"), 
          sum(bin1.pr$site=="ucsf_pr", na.rm=T)/sum(pr.all$site == "ucsf_pr"), 
          sum(bin1.pr$site=="washington", na.rm=T)/sum(pr.all$site == "washington"), 
          sum(bin1.pr$site=="washington_tgp", na.rm=T)/sum(pr.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="Rsq [0.00 - 0.25]")
barplot(c(sum(bin2.pr$site=="jhu_abr", na.rm=T)/sum(pr.all$site == "jhu_abr"), 
          sum(bin2.pr$site=="ucsf_pr", na.rm=T)/sum(pr.all$site == "ucsf_pr"), 
          sum(bin2.pr$site=="washington", na.rm=T)/sum(pr.all$site == "washington"), 
          sum(bin2.pr$site=="washington_tgp", na.rm=T)/sum(pr.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="Rsq [0.25 - 0.50]")
barplot(c(sum(bin3.pr$site=="jhu_abr", na.rm=T)/sum(pr.all$site == "jhu_abr"), 
          sum(bin3.pr$site=="ucsf_pr", na.rm=T)/sum(pr.all$site == "ucsf_pr"), 
          sum(bin3.pr$site=="washington", na.rm=T)/sum(pr.all$site == "washington"), 
          sum(bin3.pr$site=="washington_tgp", na.rm=T)/sum(pr.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="Rsq [0.50 - 0.75]")
barplot(c(sum(bin4.pr$site=="jhu_abr", na.rm=T)/sum(pr.all$site == "jhu_abr"), 
          sum(bin4.pr$site=="ucsf_pr", na.rm=T)/sum(pr.all$site == "ucsf_pr"), 
          sum(bin4.pr$site=="washington", na.rm=T)/sum(pr.all$site == "washington"), 
          sum(bin4.pr$site=="washington_tgp", na.rm=T)/sum(pr.all$site == "washington_tgp")),
        legend.text=c("jhu_abr", "ucsf_pr", "washington", "washington_tgp"),
        args.legend = list(x = "bottom"),
        main="Rsq [0.75 - 1.00]")

```

### Boxplots of recall by site

#### Overall

```{r}
boxplot(recall ~ site, data=pr.all)
```

#### Split into 4 Rsq bins

```{r}
boxplot(recall ~ site, data=bin1.pr, main="Rsq [0.00 - 0.25]")
boxplot(recall ~ site, data=bin2.pr, main="Rsq (0.25 - 0.50]")
boxplot(recall ~ site, data=bin3.pr, main="Rsq (0.50 - 0.75]")
boxplot(recall ~ site, data=bin4.pr, main="Rsq (0.75 - 1.00]")
```

### Boxplots of accuracy for MAF BINs 0.005, 0.01, 0.05, 0.1, 0.5

#### Overall

```{r}
boxplot(prop_match ~ site, data=acc.all)
```

#### Split into MAF BINs

```{r}
par(mfrow=c(3,2))

bin1.acc <- acc.all[(acc.all$MAF > 0) & (acc.all$MAF<= 0.005),]
bin2.acc <- acc.all[(acc.all$MAF > 0.005) & (acc.all$MAF<= 0.01),]
bin3.acc <- acc.all[(acc.all$MAF > 0.01) & (acc.all$MAF<= 0.05),]
bin4.acc <- acc.all[(acc.all$MAF > 0.05) & (acc.all$MAF<= 0.1),]
bin5.acc <- acc.all[(acc.all$MAF > 0.1) & (acc.all$MAF<= 0.5),]

boxplot(prop_match ~ site, data=bin1.acc, main="MAF 0 - 0.005")
boxplot(prop_match ~ site, data=bin2.acc, main="MAF 0.005 - 0.01")
boxplot(prop_match ~ site, data=bin3.acc, main="MAF 0.01 - 0.05")
boxplot(prop_match ~ site, data=bin4.acc, main="MAF 0.05 - 0.10")
boxplot(prop_match ~ site, data=bin5.acc, main="MAF 0.1 - 0.5")

```

### Boxplots of precision for MAF BINs 0.005, 0.01, 0.05

#### Overall

```{r}
boxplot(precision ~ site, data=pr.all)
```

#### Split into MAF BINs

```{r}
bin1.pr <- pr.all[(pr.all$MAF > 0) & (pr.all$MAF<= 0.005),]
bin2.pr <- pr.all[(pr.all$MAF > 0.005) & (pr.all$MAF<= 0.01),]
bin3.pr <- pr.all[(pr.all$MAF > 0.01) & (pr.all$MAF<= 0.05),]

par(mfrow=c(2,2))
boxplot(precision ~ site, data=bin1.pr, main="MAF 0 - 0.005")
boxplot(precision ~ site, data=bin2.pr, main="MAF 0.005 - 0.01")
boxplot(precision ~ site, data=bin3.pr, main="MAF 0.01 - 0.05")
```

### Boxplots of recall for MAF BINs 0.005, 0.01, 0.05

#### Overall

```{r}
boxplot(recall ~ site, data=pr.all)
```

#### Split into MAF BINs

```{r}
par(mfrow=c(2,2))
boxplot(recall ~ site, data=bin1.pr, main="MAF 0 - 0.005")
boxplot(recall ~ site, data=bin2.pr, main="MAF 0.005 - 0.01")
boxplot(recall ~ site, data=bin3.pr, main="MAF 0.01 - 0.05")
```

### Is the TGP IL33 and ST2 regions just as dense as for CAAPA? Are the new ILL33 SNPs in this data?
